## EX 3.- PDP to explain the price of a house.
### EXERCISE:
Apply the previous concepts to predict the price of a house from the database kc_house_data.csv. In this case, use again a random forest approximation for the prediction based on the features bedrooms, bathrooms, sqft_living, sqft_lot, floors and yr_built. 
Use the partial dependence plot to visualize the relationships the model learned.

BE CAREFUL: due to the size, extract a set of random samples from the BBDD before generating the data for the Partial Dependency Plot. 

We have to follow the same process as we did in exercise number 1, with the only difference that here we should select some of the features and not all; and we need to made a sample of 500 observations.
```{r, warning=FALSE}
library(randomForest) 
library(plyr) 
library(dplyr)
library(caret)

house <- read.csv("kc_house_data.csv")

set.seed(123)
df_sample <- house[sample(1:nrow(house), 500), ]

#Seleccionar las columnas relevantes para el modelo
X <- df_sample[, c("bedrooms", "bathrooms", "sqft_living", "sqft_lot", "floors", "yr_built")]
y <- df_sample$price

#Crear una partición de los datos en train y test
#80% de datos para entrenamiento y 20% para test
set.seed(123)
indices <- sample(2, nrow(X), replace = TRUE, prob = c(0.8, 0.2))
trainX <- X[indices == 1, ]
trainY <- y[indices == 1]
testX <- X[indices == 2, ]
testY <- y[indices == 2]

#Crear el modelo de Random Forest
rf_model <- randomForest(trainY ~ ., data = trainX)

```

### QUESTION:
Analyse the influence of bedrooms, bathrooms, sqft_living and floors on the predicted price.
```{r}
partialPlot(rf_model, df_sample, x.var=bedrooms)
partialPlot(rf_model, df_sample, x.var=bathrooms)
partialPlot(rf_model, df_sample, x.var=sqft_living)
partialPlot(rf_model, df_sample, x.var=floors)
```
 
 Let us now interpret the results. 

Again as in exercise number 1 we are looking at the effect of a variable, in this case: bedrooms, bathrooms, sqft_living and floors on the price of a house. To refresh ideas, the Y-axis shows the predicted price of the house in question, while the X-axis shows the variable chosen at each point in time.

As usual, all the plots are increasing, since the price of a house will increase as the number of bedrooms, bathrooms, living space and floors in the house increase. The only perhaps surprising thing is that we don't see a big increase in the price of the house in the case of the increase in bathrooms until we get to the houses with 6 bathrooms, where we do see a big increase.