---
title: "Deployment"
author: "IvanL"
date: "3/5/2023"
output: html_document
---

# DEPLOYMENT
Lautaro Paniati Altamirano
Pablo Ramon Tadghighi
Ivan Lopez Llorens


## EX 1.- One dimensional Partial Dependence Plot.
The partial dependence plot shows the marginal effect of a feature on the predicted outcome of a previously fit model. 
 
### EXERCISE:
Apply PDP to the regression example of predicting bike rentals. Fit a random forest approximation for the prediction of bike rentals (cnt). Use the partial dependence plot to visualize the relationships the model learned. Use the slides shown in class as model.  

We load the necessary libraries for the exercise and modify the bike_rental dataset as we did in the previous sessions.
```{r, warning=False}
library(randomForest)
library(ggplot2)

bike_rental <- read.csv("day.csv")

bike_rental$season1 <- ifelse(bike_rental$season == 1, 1, 0)
bike_rental$season2 <- ifelse(bike_rental$season == 2, 1, 0)
bike_rental$season3 <- ifelse(bike_rental$season == 3, 1, 0)
bike_rental$season4 <-ifelse(bike_rental$season == 4, 1, 0)

bike_rental <- subset(bike_rental, select = -c(season))

bike_rental$misty <- ifelse(bike_rental$weathersit == 2, 1, 0)

bike_rental$rain <- ifelse(bike_rental$weathersit %in% c(3, 4), 1, 0)

bike_rental$temp <- bike_rental$temp * 47 - 8
bike_rental$hum <- bike_rental$hum * 100
bike_rental$windspeed <- bike_rental$windspeed * 67

bike_rental$days_since_2011 <- as.numeric(as.Date(bike_rental$dteday, format="%Y-%m-%d") - as.Date("2011-01-01"))

```

Now, we simply do what the exercise asks us. We create the randomForest object with the bike rental dataset and whose variable to predict is cnt, as indicated in the statement.
```{r, warning=FALSE}
cnt = bike_rental$cnt
sol = randomForest(bike_rental, cnt)
# Now we should use the function partialPlot to see the relationships between the features and the feature to be predicted. In the next chunks we will see some of them 
#partialPlot(sol, bike_rental, x.var="the feature to show the relationship")
```

### QUESTION:
Analyse the influence of days since 2011, temperature, humidity and wind speed on the predicted bike counts.

Now the schema to follow is: partialPlot(object randomForest, dataset, x.var=feature)
```{r, warning=FALSE}
partialPlot(sol, bike_rental, x.var=days_since_2011)
partialPlot(sol, bike_rental, x.var=temp)
partialPlot(sol, bike_rental, x.var=hum)
partialPlot(sol, bike_rental, x.var=windspeed)
```

We can now see the results of the various PDPs. Of course, all weather effects affect bicycle rental in one way or another, because it is an activity that is uncomfortable to carry out in certain conditions.

The graphs follow the following pattern: the Y-axis is the number of predicted rentals (cnt) and the X-axis the corresponding feature in each case. It is simply a relationship in which we see whether the higher or lower the value of the variable we want, the higher or lower the number of rents.

Let's go in order, looking at the influence of the variable days_since_2011 we see that it has been increasing as there has been more difference, since it is increasing, with some steps. With the case of the temperature we see that it is increasing as the temperature increases, although when it reaches a very high temperature, approx. 35 degrees, it starts to decrease. With rain and humidity something similar happens, if it rains or the humidity is high, less bicycles will be rented.



## EX 2.- Bidimensional Partial Dependency Plot.
### EXERCISE:
Generate a 2D Partial Dependency Plot with humidity and temperature to predict the number of bikes rented depending on those parameters.

BE CAREFUL: due to the size, extract a set of random samples from the BBDD before generating the data for the Partial Dependency Plot. 

Show the density distribution of both input features with the 2D plot as shown in the class slides. 

TIP: Use geom_tile() to generate the 2D plot. Set width and height to avoid holes. 

### QUESTION:
Interpret the results.

```{r, warning=FALSE}
library(dplyr)
#Extract random samples 
muestras <- sample_n(bike_rental, size = 250)

ggplot(muestras, aes(x=hum, y=temp)) +
  geom_tile(width = 0.3, height = 0.3)

#We show the relationships between these features and cnt in the next code 
ggplot(muestras, aes(x=hum, y=temp)) +
  geom_point(aes(colour=cnt)) +
  geom_tile(width = 0.3, height = 0.3)

```

The interpretation in this case is quite simple: the Y-axis corresponds to the temperature values, while the X-axis corresponds to the humidity values. In addition, on the right we see a legend with a colour scale from highest to lowest bicycle rental. 

It is enough to choose a point on the graph and see the colour of the one we have. If it is lighter, it means that in those conditions of temperature and humidity there is a greater number of rentals. Logically, the lower the humidity and the higher the temperature, the more bicycle rentals are produced.



## EX 3.- PDP to explain the price of a house.
### EXERCISE:
Apply the previous concepts to predict the price of a house from the database kc_house_data.csv. In this case, use again a random forest approximation for the prediction based on the features bedrooms, bathrooms, sqft_living, sqft_lot, floors and yr_built. 
Use the partial dependence plot to visualize the relationships the model learned.

BE CAREFUL: due to the size, extract a set of random samples from the BBDD before generating the data for the Partial Dependency Plot. 

We have to follow the same process as we did in exercise number 1, with the only difference that here we should select some of the features and not all; and we need to made a sample of 500 observations.
```{r, warning=FALSE}
library(randomForest) 
library(plyr) 
library(dplyr)
library(caret)

house <- read.csv("kc_house_data.csv")

set.seed(123)
df_sample <- house[sample(1:nrow(house), 500), ]

#Seleccionar las columnas relevantes para el modelo
X <- df_sample[, c("bedrooms", "bathrooms", "sqft_living", "sqft_lot", "floors", "yr_built")]
y <- df_sample$price

#Crear una partición de los datos en train y test
#80% de datos para entrenamiento y 20% para test
set.seed(123)
indices <- sample(2, nrow(X), replace = TRUE, prob = c(0.8, 0.2))
trainX <- X[indices == 1, ]
trainY <- y[indices == 1]
testX <- X[indices == 2, ]
testY <- y[indices == 2]

#Crear el modelo de Random Forest
rf_model <- randomForest(trainY ~ ., data = trainX)

```

### QUESTION:
Analyse the influence of bedrooms, bathrooms, sqft_living and floors on the predicted price.
```{r}
partialPlot(rf_model, df_sample, x.var=bedrooms)
partialPlot(rf_model, df_sample, x.var=bathrooms)
partialPlot(rf_model, df_sample, x.var=sqft_living)
partialPlot(rf_model, df_sample, x.var=floors)
```
 
 Let us now interpret the results. 

Again as in exercise number 1 we are looking at the effect of a variable, in this case: bedrooms, bathrooms, sqft_living and floors on the price of a house. To refresh ideas, the Y-axis shows the predicted price of the house in question, while the X-axis shows the variable chosen at each point in time.

As usual, all the plots are increasing, since the price of a house will increase as the number of bedrooms, bathrooms, living space and floors in the house increase. The only perhaps surprising thing is that we don't see a big increase in the price of the house in the case of the increase in bathrooms until we get to the houses with 6 bathrooms, where we do see a big increase.