---
title: "Deployment"
date: "3/5/2023"
output: html_document
---

# DEPLOYMENT
Lautaro Paniati Altamirano
Pablo Ramon Tadghighi
Ivan Lopez Llorens


## EX 1.- One dimensional Partial Dependence Plot.
The partial dependence plot shows the marginal effect of a feature on the predicted outcome of a previously fit model. 
 
### EXERCISE:
Apply PDP to the regression example of predicting bike rentals. Fit a random forest approximation for the prediction of bike rentals (cnt). Use the partial dependence plot to visualize the relationships the model learned. Use the slides shown in class as model.  

We load the necessary libraries for the exercise and modify the bike_rental dataset as we did in the previous sessions.
```{r, warning=False}
library(randomForest)
library(ggplot2)
bike_rental <- read.csv("day.csv")
bike_rental$season1 <- ifelse(bike_rental$season == 1, 1, 0)
bike_rental$season2 <- ifelse(bike_rental$season == 2, 1, 0)
bike_rental$season3 <- ifelse(bike_rental$season == 3, 1, 0)
bike_rental$season4 <-ifelse(bike_rental$season == 4, 1, 0)
bike_rental <- subset(bike_rental, select = -c(season))
bike_rental$misty <- ifelse(bike_rental$weathersit == 2, 1, 0)
bike_rental$rain <- ifelse(bike_rental$weathersit %in% c(3, 4), 1, 0)
bike_rental$temp <- bike_rental$temp * 47 - 8
bike_rental$hum <- bike_rental$hum * 100
bike_rental$windspeed <- bike_rental$windspeed * 67
bike_rental$days_since_2011 <- as.numeric(as.Date(bike_rental$dteday, format="%Y-%m-%d") - as.Date("2011-01-01"))
```

Now, we simply do what the exercise asks us. We create the randomForest object with the bike rental dataset and whose variable to predict is cnt, as indicated in the statement.
```{r, warning=FALSE}
cnt = bike_rental$cnt
sol = randomForest(bike_rental, cnt)
# Now we should use the function partialPlot to see the relationships between the features and the feature to be predicted. In the next chunks we will see some of them 
#partialPlot(sol, bike_rental, x.var="the feature to show the relationship")
```

### QUESTION:
Analyse the influence of days since 2011, temperature, humidity and wind speed on the predicted bike counts.

Now the schema to follow is: partialPlot(object randomForest, dataset, x.var=feature)
```{r, warning=FALSE}
partialPlot(sol, bike_rental, x.var=days_since_2011)
partialPlot(sol, bike_rental, x.var=temp)
partialPlot(sol, bike_rental, x.var=hum)
partialPlot(sol, bike_rental, x.var=windspeed)
```

We can now see the results of the various PDPs. Of course, all weather effects affect bicycle rental in one way or another, because it is an activity that is uncomfortable to carry out in certain conditions.

The graphs follow the following pattern: the Y-axis is the number of predicted rentals (cnt) and the X-axis the corresponding feature in each case. It is simply a relationship in which we see whether the higher or lower the value of the variable we want, the higher or lower the number of rents.

Let's go in order, looking at the influence of the variable days_since_2011 we see that it has been increasing as there has been more difference, since it is increasing, with some steps. With the case of the temperature we see that it is increasing as the temperature increases, although when it reaches a very high temperature, approx. 35 degrees, it starts to decrease. With rain and humidity something similar happens, if it rains or the humidity is high, less bicycles will be rented.